Wide-Field Signatures in Redshifted 21~cm Power Spectra

### 2015-03-18 ms.tex
Reorganize list of authors and affiliations
From af1b5c4:
============

In ms.tex,

(*) Reorganize list of authors and affiliations
(*) Minor changes in text

\def\MIT{\altaffilmark{9}}
\def\MITtxt{\altaffiltext{9}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\Curtin{\altaffilmark{10}}
\def\Curtintxt{\altaffiltext{10}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}

\def\Victoria{\altaffilmark{11}}
\def\Victoriatxt{\altaffiltext{11}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{12}}
\def\UWisctxt{\altaffiltext{12}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}

\def\UMichigan{\altaffilmark{13}}
\def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}

\def\UMelbourne{\altaffilmark{14}}
\def\UMelbournetxt{\altaffiltext{14}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}

\def\USydney{\altaffilmark{15}}
\def\USydneytxt{\altaffiltext{15}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}

@@

\def\RRI{\altaffilmark{18}}
\def\RRItxt{\altaffiltext{18}{Raman Research Institute, Bangalore 560080, India}}

\def\NRAO{\altaffilmark{19}}
\def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

\def\UWA{\altaffilmark{20}}
\def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}

@@

\title{Wide-Field Effects in Redshifted 21~cm Power Spectra}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
N.~Barry\UW,
A.~P.~Beardsley\UW,
G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
F.~Briggs\ANU$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
B.~E.~Corey\Haystack, 
% A.~A.~Deshpande\RRI, 
A.~de~Oliveira-Costa\MIT,
Joshua~S.~Dillon\MIT,
D.~Emrich\Curtin,
% B.~M.~Gaensler\USydney$^,$\CAASTRO, 
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
N.~Hurley-Walker\Curtin,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
J.~C.~Kasper\UMichigan$^,$\CfA, 
Han-Seek Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
M.~J.~Lynch\Curtin, 
B.~McKinley\UMelbourne$^,$\CAASTRO,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
A.~R.~Offringa\ANU$^,$\CAASTRO, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
Sourabh~Paul\RRI,
B.~Pindor\UMelbourne$^,$\CAASTRO,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
A.~E.~E.~Rogers\Haystack, 
A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
Shiv~K.~Sethi\RRI,
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UWtxt
\SKASAtxt
\RUtxt
\CfAtxt
\ANUtxt
\CAASTROtxt
\Haystacktxt
\MITtxt
\Curtintxt
\Victoriatxt
\UWisctxt
\UMichigantxt
\UMelbournetxt
\USydneytxt
\CASStxt
\Tatatxt
\RRItxt
\NRAOtxt
\UWAtxt
\myemailtxt

@@

While probing H~{\sc i} in the epoch of reionization (EoR), through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature. By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$. This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.

@@

Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio continuum emission from foreground objects. This poses perhaps the greatest challenge to EoR experiments and therefore merits a detailed characterization of foreground signatures in order to separate them from the desired signal.

In a recent study, through the use of models for an all-sky foreground and the instrument, the role of wide-field nature of modern radio interferometric measurements, hitherto unpredicted, has emerged. It is referred to as the {\it pitchfork} signature in the delay spectral domain, and is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon. The latter is due to the highly non-linear mapping between geometric delays and subtended solid angles besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions. Owing to its localization in delay spectral domain, it is a leading cause of contamination in Fourier modes most sensitive to the cosmological H~{\sc i} signal. This feature could not be confirmed in individual MWA snapshot due to the high level of thermal fluctuations.

>>>>

\def\RRI{\altaffilmark{9}}
\def\RRItxt{\altaffiltext{9}{Raman Research Institute, Bangalore 560080, India}}

\def\MIT{\altaffilmark{10}}
\def\MITtxt{\altaffiltext{10}{MIT Kavli Institute for Astrophysics and Space Research, Cambridge, MA 02139, USA}}

\def\USydney{\altaffilmark{11}}
\def\USydneytxt{\altaffiltext{11}{The University of Sydney, Sydney Institute for Astronomy, School of Physics, NSW 2006, Australia}}

\def\Curtin{\altaffilmark{12}}
\def\Curtintxt{\altaffiltext{12}{International Centre for Radio Astronomy Research, Curtin University, Perth, WA 6845, Australia}}

\def\Victoria{\altaffilmark{13}}
\def\Victoriatxt{\altaffiltext{13}{Victoria University of Wellington, School of Chemical \& Physical Sciences, Wellington 6140, New Zealand}}

\def\UWisc{\altaffilmark{14}}
\def\UWisctxt{\altaffiltext{14}{University of Wisconsin--Milwaukee, Department of Physics, Milwaukee, WI 53201, USA}}

\def\UMelbourne{\altaffilmark{15}}
\def\UMelbournetxt{\altaffiltext{15}{The University of Melbourne, School of Physics, Parkville, VIC 3010, Australia}}

@@

% \def\NRAO{\altaffilmark{19}}
% \def\NRAOtxt{\altaffiltext{19}{National Radio Astronomy Observatory, Charlottesville and Greenbank, USA}}

% \def\UMichigan{\altaffilmark{13}}
% \def\UMichigantxt{\altaffiltext{13}{University of Michigan, Department of Atmospheric, Oceanic and Space Sciences, Ann Arbor, MI 48109, USA}}

% \def\UWA{\altaffilmark{20}}
% \def\UWAtxt{\altaffiltext{20}{International Centre for Radio Astronomy Research, University of Western Australia, Crawley, WA 6009, Australia}}

@@

\title{Wide-Field Signatures in Redshifted 21~cm Power Spectra}

@@

%% Author list
\author{
%% Lead Authors
Nithyanandan~Thyagarajan\ASU\myemail,
Daniel~C.~Jacobs\ASU,
Judd~D.~Bowman\ASU,
N.~Barry\UW,
A.~P.~Beardsley\UW,
G.~Bernardi\SKASA$^,$\RU$^,$\CfA,
F.~Briggs\ANU$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
% B.~E.~Corey\Haystack, 
A.~A.~Deshpande\RRI, 
A.~de~Oliveira-Costa\MIT,
Joshua~S.~Dillon\MIT,
% D.~Emrich\Curtin,
B.~M.~Gaensler\USydney$^,$\CAASTRO, 
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
% R.~Goeke\MIT,
L.~J.~Greenhill\CfA,
B.~J.~Hazelton\UW, 
J.~N.~Hewitt\MIT,
N.~Hurley-Walker\Curtin,
M.~Johnston-Hollitt\Victoria,
D.~L.~Kaplan\UWisc, 
% J.~C.~Kasper\UMichigan$^,$\CfA, 
Han-Seek Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
% E.~Kratzenberg\Haystack, 
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
% M.~J.~Lynch\Curtin, 
B.~McKinley\UMelbourne$^,$\CAASTRO,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
A.~R.~Offringa\ANU$^,$\CAASTRO, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
Sourabh~Paul\RRI,
B.~Pindor\UMelbourne$^,$\CAASTRO,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
% A.~E.~E.~Rogers\Haystack, 
% A.~Roshi\NRAO, 
N.~Udaya~Shankar\RRI, 
Shiv~K.~Sethi\RRI,
K.~S.~Srivani\RRI, 
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
% M.~Waterson\Curtin$^,$\ANU,
R.~B.~Wayth\Curtin$^,$\CAASTRO, 
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
% A.~R.~Whitney\Haystack, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
% C.~Wu\UWA,
J.~S.~B.~Wyithe\UMelbourne$^,$\CAASTRO
}

%Institutional footnotes (typeset, then rearrange here to be in order)
\ASUtxt
\UWtxt
\SKASAtxt
\RUtxt
\CfAtxt
\ANUtxt
\CAASTROtxt
\Haystacktxt
\RRItxt
\MITtxt
\USydneytxt
\Curtintxt
\Victoriatxt
\UWisctxt
\UMelbournetxt
\CASStxt
\Tatatxt
\myemailtxt
% \NRAOtxt
% \UMichigantxt
% \UWAtxt

@@

While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature. By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$. This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions.

@@

Fluctuations of redshifted H~{\sc i} from the reionization epoch are extremely faint relative to the radio foregrounds. This poses perhaps the greatest challenge to EoR experiments and thus merits a detailed characterization in order to separate them from the desired cosmological H~{\sc i} signal.

In a recent study, through the use of all-sky foreground and instrument models, the role of wide-field nature of radio interferometric measurements, hitherto unpredicted, has emerged. Referred to as the {\it pitchfork} signature in the delay spectral domain, it is characterized by significant foreground power in the primary field of view and an enhancement in power near the horizon. The latter is due to the highly nonlinear mapping between geometric delays and subtended solid angles, besides an increase in sensitivity to larger scales caused by foreshortening of baseline lengths along these directions. Owing to its localization in the delay domain, it is a leading cause of contamination in Fourier modes most sensitive to the EoR H~{\sc i} signal. This feature could not be confirmed in single MWA snapshots due to large thermal fluctuations.
